---
title: "Exercise 2"
author: "David Scolari"
date: "2/21/2022"
output: html_document
---
<style>
    body { 
      background-color: black;
      color: white}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r source, include=FALSE}
library(here)
path <- here()
source(file.path(path, "code", "lib.R"))
source(file.path(path, "code", "ex_2_1.R"))
```

![CAPTION HERE: Give the figure an informative caption in which you explain what is shown in the figure and address the following questions, citing evidence from the figure. Does the hour of peak boardings change from day to day, or is it broadly similar across days? Why do you think average boardings on Mondays in September look lower, compared to other days and months? Similarly, why do you think average boardings on Weds/Thurs/Fri in November look lower?](`r file.path(path, "output", "boardings_hour.png")`)

![CAPTION HERE: Give the figure an informative caption in which you explain what is shown in the figure and answer the following question, citing evidence from the figure. When we hold hour of day and weekend status constant, does temperature seem to have a noticeable effect on the number of UT students riding the bus?](`r file.path(path, "output", "boardings_temp.png")`)


