---
title: "Data Mining: Exercise 1 Solutions"
author: "David Scolari"
date: "2/11/2022"
output: md_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r source, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# set user's unique path to the ECO395M directory
# new users must edit here
path <- "/Users/davidscolari/Dropbox/grad_school/3_Spring22/ECO395M"

# make path to sub-directories
path_data <- file.path(path, "data")
path_code <- file.path(path, "solutions", "code")
path_out <- file.path(path, "solutions", "output")

# source code for each question
source(file.path(path_code, "ex1_lib.R"))
source(file.path(path_code, "ex1_1_abia.R"))
source(file.path(path_code, "ex1_2_billboard.R"))
source(file.path(path_code, "ex1_3_olympics_top20.R"))
source(file.path(path_code, "ex1_4_sclass.R"))
```

## Exercise 1

```{r figure_1, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
season_sofly
```

The above bar panels show how flight delays and cancellations of Austin Airport (AUS) flights change by time of day as well as by season. A few trends can be identified from this figure. First, flight delays appear to increase as the day goes on, while cancellations appear to be more prevalent in the mornings and less in the evenings. Winter seems to have more cancellations and longer delays across all times while Fall seems to have less. The best time to fly depends on whether someone wants to avoid a flight delay or a cancellation. Fall mornings have the shortest delays while Fall night flights are least likily to get canceled.

## Exercise 2

### Part A

```{r top10_1958_2021, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
kable(as.data.frame(top10_1958_2021), 
      caption = "Top 10 Songs: 1958 - 2021")
```

The above table show the 10 songs with the most weeks spent on the Billboard Hot 100 song list. 

### Part B

```{r musical_diversity_tplot, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
musical_diversity_tplot
```

This is a time plot of the number of unique songs to make the Billboard Hot 100 between the years 1959-2020. It is interesting to see the number of unique songs decline from it's peak in the 1960s, reach bottom in the early 2000s, and start to climb again through 2020. 

### Part C

```{r tenwk_hits_bplot, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
tenwk_hits_bplot
```

These are the 19 artists who had more than 30 songs which stayed on the Hot 100 for at least 10 consecutive weeks between 1958 and mid-2021.

## Exercise 3

### Part A

The 95th percentile of heights for female competitors across all Athletics events is Volleyball with an average height of `r round(sport_heights$height[1], digits = 3)` cm.

### Part B
`r event_sdheights$event[1]` is the single women's event had the greatest variability in competitor's heights across the entire history of the Olympics, with a standard deviation of `r round(event_sdheights$sd_height[1], digits = 3)` cm.



### Part C

```{r swim_age_tplot, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
swim_age_tplot
```

The above time plot shows how the average age of male and female swimmers at the olympics has increased over time. The male swimmer ages trend steadily upward from early 20s in the 1890s to mid-late 20s in the 2010s. Female ages, on the other hand, trend sharply upward between the 1920s and the late 1940s, level off in the mid 1900s, and climb again toward the turn of the century.

## Exercise 4

```{r sclass_knn_plots, echo=FALSE, warning=FALSE, message=FALSE}
scrmse_knn_plots
scfit_knn_plots
```

The above 4 panels show the results of a k-nearest-neighbors (KNN) model trained to predict prices of two models of Mercedes S-Class automobiles based on their mileage. The two models, 350 and 63 AMG, are treated separately. The data for each model receives an 80/20 train/test split. Several different k values are used to train the KNN and determine the k that results in the lowest RMSE when plotted against the testing data.. For a particular train/test split (shown above), the k value that results in the lowest rmse for the 350 model is k = `r sc350_rmse$k[1]` and k = `r sc63amg_rmse$k[1]` for the 63 AMG. 

Across most train/test splits, the optimal k for the 63 AMG model is larger than the optimal k for the 350 model. This is because the 350 model dataset only has 416 observations while the 63 AMG model has 1413 observations. This means that for a given point in the 350 model data, the k nearest neighbors are likely spread out over a wide mileage range, making bias a problem even at relatively small values of k. On the other hand, the k nearest neighbors for a point in the 63 AMG data are likely to be close by in mileage, so the KNN can get away with a larger k, making the model smoother before bias becomes a problem.